---
title: "weka abundance"
output: html_document
date: '2022-08-12'
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load libraries

```{r}
install.packages("tidyverse")
install.packages("permute")
install.packages("lattice")
library(tidyverse)
library(ggplot2)
library(reshape2)
library(vegan)
install.packages("zoo")
library(zoo)
```

Table

for R on citrix: 
weka_raw <- read_csv("\\\\student.otago.ac.nz/mds/Profiles-V2/l/limla371/RedirectedFolders/Documents/lauren_data.csv")
[rows,columns]
```{r}
library(readr)
weka_raw <- read_csv("/Users/laurenlim/Desktop/lauren_data.csv")
weka_raw <- weka_raw[1:6,]
meta_data <- weka_raw[,2:3]
rownames(meta_data) <- weka_raw$Library
meta_data <- meta_data%>%mutate(age = as.factor(Spur.age), buffer =  as.factor(Storage.buffer))
```

```{r}
weka_raw_vertebrateonly <- weka_raw [,1:6]
meta_data_v <- weka_raw_vertebrateonly[,2:3]
rownames(meta_data_v) <- weka_raw_vertebrateonly$Library
meta_data_v <- meta_data_v%>%mutate(age = as.factor(Spur.age), buffer =  as.factor(Storage.buffer))
weka_norm_v <- sweep(weka_raw_vertebrateonly[,-c(1:3)], 1, rowSums(weka_raw_vertebrateonly[,-c(1:3)]),"/")
rowSums(weka_norm_v)
rownames(weka_norm_v) <- weka_raw_vertebrateonly$Library
t_weka_v <- t(weka_norm_v)
melt_t_weka_v <- melt(t_weka_v)
colnames(melt_t_weka_v) <- c("Family","Library","Abundance")

ggplot(melt_t_weka_v, aes(fill=Family,y=Abundance, x=Library)) +             
  geom_bar(position="fill", stat="identity")
```

```{r}
weka_norm <- sweep(weka_raw[,-c(1:3)], 1, rowSums(weka_raw[,-c(1:3)]),"/")
rowSums(weka_norm)
rownames(weka_norm) <- weka_raw$Library

#transpose
t_weka <- t(weka_norm)

#melt
melt_t_weka <- melt(t_weka)

colnames(melt_t_weka) <- c("Family","Library","Abundance")

#plot
ggplot(melt_t_weka, aes(fill=Family,y=Abundance, x=Library)) +             
  geom_bar(position="fill", stat="identity")

#split by V and I, change colour
```

```{r}
shannon <- apply(weka_norm, 1, diversity, index="shannon")
shannon

#try simpson and others

#boxplot
shannon_matrix <- as.matrix(shannon)
shannon_matrix_age <- cbind (shannon_matrix, meta_data$age)
shannon_matrix_age_buffer <- cbind(shannon_matrix_age, meta_data$buffer)
colnames(shannon_matrix_age_buffer) <- c("Shannon", "Age", "Buffer")

#extract age
spur_age1 <- shannon_matrix_age_buffer [1:2,]
spur_age2 <- shannon_matrix_age_buffer [3:4,]
spur_age3 <- shannon_matrix_age_buffer [5:6,]

shannon_matrix <- t(as.matrix(merge(zoo(spur_age1[,1]), zoo(spur_age2[,1]), zoo(spur_age3[,1]))))
class(shannon_matrix) <- "numeric"

rownames(shannon_matrix) <- c("S1", "S2", "S3")

t_shannon_matrix <- t(shannon_matrix)
melt_t_shannon_matrix <- melt(t_shannon_matrix)

colnames(melt_t_shannon_matrix) <- c("Buffer", "Spur Age", "Shannon")

#plot
ggplot(melt_t_shannon_matrix, aes(x=`Spur Age`, y= Shannon, fill=`Spur Age`)) +
  geom_boxplot() + geom_jitter (colout="black", size=2, alpha=0.2) + ggtitle ("Shannon by Spur Age")




#extract buffer
RNA_DNA_shield <- shannon_matrix_age_buffer[c(1,3,5)]
RNA_Later <- shannon_matrix_age_buffer [c(2,4,6)]

shannon_matrix <- t(as.matrix(merge(zoo(RNA_DNA_shield), zoo(RNA_Later))))
class(shannon_matrix) <- "numeric"

rownames(shannon_matrix) <- c("RNA/DNA Shield", "RNA Later")

t_shannon_matrix <- t(shannon_matrix)
melt_t_shannon_matrix <- melt(t_shannon_matrix)

colnames(melt_t_shannon_matrix) <- c("Spur Age", "Buffer", "Shannon")

#plot
p <- ggplot(melt_t_shannon_matrix, aes(x=Buffer, y= Shannon, fill=Buffer)) +
  geom_boxplot() + geom_jitter (colour="black", size=2, alpha=0.2) + ggtitle ("Shannon by Buffer")

p <- p + stat_compare_means(method = "t.test")

p + stat_compare_means( aes(label = ..p.signif..)

p
```


```{r}

```




