---
title: "weka_buffer_plots"
output: html_document
date: "2022-09-01"
editor_options: 
  chunk_output_type: console
---
```{r}
#making a barplot
raw_reads <- c(78541734, 79982212, 82062117, 93366714,85165521, 85246606)

barplot(raw_reads,
xlab = "Library",
ylab = "Number of raw reads",
names.arg = c("S1", "S2", "S3", "S1", "S2", "S3"),
horiz = TRUE)
```

```{r}
#back to abundance plots
install.packages("tidyverse")
install.packages("permute")
install.packages("lattice")
install.packages("zoo")
library(tidyverse)
library(ggplot2)
library(reshape2)
library(vegan)
library(zoo)
library(readr)
install.packages("ggpubr")
library(ggpubr)
```

```{r}
buffer_boxplot <- read_csv("/Users/laurenlim/Desktop/weka_buffer_boxplot.csv")
buffer_boxplot <- buffer_boxplot[-c(21, 22),]
buffer_boxplot <- buffer_boxplot[,c(3, 5)]
colnames(buffer_boxplot) <- c("buffer","concentration")

p <- ggplot(buffer_boxplot, aes(x=buffer, y= concentration, fill=buffer)) + geom_boxplot() + geom_jitter (colour="black", size=2, alpha=0.2) + ggtitle ("RNA concentrations")

p <- p + stat_compare_means(method = "t.test")

p + stat_compare_means( aes(label = ..p.signif..), 
                        label.x = 1.5, label.y = 40)
```

concentration <- buffer_boxplot[,2]
buffer <- buffer_boxplot[,1]

concentration_matrix <- as.matrix(concentration)
DNA_RNA_shield <- concentration_matrix[(1:20),]
RNA_Later <- concentration_matrix[(21:42),]

t_concentration_matrix <- t(as.matrix(merge(zoo(DNA_RNA_shield), zoo(RNA_Later))))
class(concentration_matrix) <- "numeric"

rownames(t_concentration_matrix) <- c("DNA/RNA Shield", "RNA Later")

t_concentration_matrix <- t(t_concentration_matrix)
```

```{r}



buffer_matrix <- cbind (concentration_matrix, buffer)

DNA_RNA_shield <- buffer_boxplot_matrix[(1:20),]
RNA_Later <- buffer_boxplot_matrix[(21:42),]

```



